Model LF

### 2022-10-31 max_dp endogen stød.Rmd
Commit

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4)
)
```

@@

```{r}
plot(tilpas_pr_00, col= "green"); lines(tilpas_pr, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(u_ds_00, col= "green"); lines(u_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(wage_trim_00, col= "green"); lines(wage_trim1, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(dp_person_00, col= "green"); lines(mean_dp_regul, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(stat_tilpas_00, col= "green", ylim= c(-0.03,0.05)); lines(stat_tilpas, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(max_dp_00, col= "green"); lines(obs_dp_q, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(wage_00, col= "green"); lines(wage, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(wage_ds_t_00, col= "green"); lines(wage_ds_t, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(prod_00, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(prod_ds_00, col= "green"); lines(prod_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(shock_kuld_00, col= "green"); lines(kuld, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(komp_r_00, col= "green"); lines(komp_r_obs1, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(kont_h_ratio_00, col= "green"); lines(kont_h_dp_person, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ur_ds_00, col= "green"); lines(ur_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(nben_h_rest_00, col= "green"); lines(nben_h_rest_obs, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

### Gengivelse
plot(yk_ds_00, ylim= c(430000, 540000), col= "green"); lines(yk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(emp_00, col= "green"); lines(emp, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(pconk_ds_00,ylim= c(210000, 250000), col= "green"); lines(pconk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ik_00, col= "green"); lines(ik, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(yd_hk_ds_00, col= "green"); lines(yd_hk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(part_00, col= "green"); lines(part, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(pc_ds_00, col= "green"); lines(pc_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(wage_ds_00, col= "green"); lines(wage_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

@@

@@

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-1500, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
((emp_07 - emp_bs7)*1000)
```

@@

```{r}
plot(((emp_06 - emp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_05 - emp_bs56)*1000), col= "black");
legend("left", legend=c("All channels except productivity", "All channels except productivity"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

```{r}
plot(((emp_06 - emp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_05 - emp_bs56)*1000), col= "black");
legend("left", legend=c("All channels max_dp", "All channels Regul"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

```{r}
plot(((emp_06b - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_07 - emp_bs7)*1000), col= "black");
legend("left", legend=c("All channels except productivity", "All channels except productivity"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

@@

**Macro effect without productivity**

@@

>>>>

COMMENT> 
BEHAVIORAL> lf_test
TSRANGE 2005 3 2020 1
EQ> lf_test = theta_00 + theta_01 * TSLAG(ur_ds,1)
COEFF> theta_00 theta_01
STORE> coe(102)

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

@@

## Baseline Scenario 1

```{r}
shock_lf_model_shock=shock_lf_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs1 <- list(

 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs1
                    )
```

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prod_bs1 = Shock_bs1$simulation$prod

xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds

net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1

ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk

ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1

c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
```

```{r}
plot(lf_bs1, col= "green"); lines(LF, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

## Baseline Scenario 7b

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs7b <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs7b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs7b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
prodk_bs7b = Shock_bs7b$simulation$prodk
tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur
```

## Scenario 0 lf

```{r}
# Define add-factor list (defining shock)
constantAdjList0 <- list(

 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
  shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_0 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList0
                    )
```

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_000 = Shock_0$simulation$komp_r
part_000 = Shock_0$simulation$part
yk_ds_000 = Shock_0$simulation$yk_ds
pc_ds_000 = Shock_0$simulation$pc_ds
wage_ds_t_000 = Shock_0$simulation$wage_ds_t
ur_ds_000 = Shock_0$simulation$ur_ds
emp_000 = Shock_0$simulation$emp
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
lf_000 = Shock_0$simulation$lf
tilpas_pr_000 = Shock_0$simulation$tilpas_pr
u_ds_000 = Shock_0$simulation$u_ds
part_000 = Shock_0$simulation$part
nben_h_000 = Shock_0$simulation$nben_h
wage_ds_000 = Shock_0$simulation$wage_ds
dp_person_000 = Shock_0$simulation$dp_person
kont_h_ratio_000 = Shock_0$simulation$kont_h_ratio

nl_g_000 = Shock_0$simulation$nl_g

yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
wage_gap1_000 = Shock_0$simulation$wage_gap1
wage_gap_000 = Shock_0$simulation$wage_gap
prod_000 = Shock_0$simulation$prod
```

@@

```{r}
plot(((unemp_07 - unemp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-300, 1500));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
((unemp_07 - unemp_bs7)*1000)
```

@@

# Scenario 7b All but prod

```{r}
# Define add-factor list (defining shock)
constantAdjList7b <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_7b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList7b
                    )

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part

prodk_07b = Shock_7b$simulation$prodk
```

```{r}
plot(((unemp_07b - unemp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Change in Unemployment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((nl_g_07b - nl_g_bs7b)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending");
lines(((nl_g_04 - nl_g_bs4)), col= "black");
lines(((nl_g_02 - nl_g_bs2)), col= "red");
lines(((nl_g_01 - nl_g_00)), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0011, 0.0015));
lines(((yk_ds_07b - yk_ds_bs7b) / yk_ds_bs7b), col= "red");
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","All channels but productivity","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red","yellow", "black","orange", "green"));
grid()
```

@@

**Macro effect without productivity and lf**

@@

**Macro effect without productivity and lf**

```{r}
change_unemp_pr_07b= (unemp_07b - unemp_bs7b)/unemp_bs7b
change_dp_person_pr_07b= (dp_person_07b - dp_person_bs7b)/dp_person_bs7b
```

```{r}
e3= change_unemp_pr_07b/change_dp_person_pr_07b;e3
```
